---
title: "Demographics"
output:
  html_document:
    toc: yes
    self_contained: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 3
    number_sections: False
    highlight: pygments
    theme: cosmo
    code_folding: "hide"
    df_print: paged
    fig_caption: true
  pdf_document:
    toc: yes
    fig_caption: true
    latex_engine: xelatex
fig.align: "center"
header-includes:
  - \usepackage{fontspec}
  - \setmainfont{AgfaRotisSansSerif}
email: koch@mpib-berlin.mpg.de
---

# Setup

```{r, message=FALSE, warning=FALSE}
packages = c("here",
             "data.table",
             "ggplot2",
             "plyr",
             "plotly",
             "dplyr",
             'viridis',
             'stringr',
             'lme4',
             'papeR',
             'binhf',
             'knitr',
             'lemon')
invisible(lapply(packages, require, character.only = TRUE))

# Get git directory 
base_path = here::here()

# Load pre-written functions
source_path = file.path(base_path, 'code', 'analysis', 'utils',
                        fsep = .Platform$file.sep)
source_files = list.files(source_path, pattern = "[.][rR]$",
                          full.names = TRUE, recursive = TRUE)
invisible(lapply(source_files, function(x) source(x)))
```


# Load demographic data

```{r}
# Load participant.tsv
file = file.path(base_path, 'bids', 'participants.tsv')
data_demo = data.table(read.table(file, sep = '\t', header = TRUE, check.names = FALSE))
```

---

# Data summary (without placebo group)

## Before exclusion

```{r}
# Convert sex variable to numeric
data_demo$female = 0
data_demo[sex == 'F']$female = 1


# Combine intervention sessions variable
data_demo$intervention = paste(data_demo$`intervention_ses-1`,
                               data_demo$`intervention_ses-2`,
                               sep = '')

# Exclude placebo group
data_demo = data_demo %>%
  dplyr::filter(intervention != 'CC') %>%
  as.data.table()

# Get statistics by group
stats_group = data_demo %>%
  group_by(group) %>%
  dplyr::summarise(n = length(age),
                   n_female = sum(female),
                   n_male = length(female) - sum(female),
                   perc_female = sum(female)/length(female),
                   age_mean = mean(age),
                   age_sd = sd(age),
                   age_low = min(age),
                   age_high = max(age))

# Get statistics by group and intervention
stats_intervention = data_demo %>%
  group_by(group, intervention) %>%
  dplyr::summarise(n = length(age),
                   n_female = sum(female),
                   n_male = length(female) - sum(female),
                   perc_female = sum(female)/length(female),
                   age_mean = mean(age),
                   age_sd = sd(age),
                   age_low = min(age),
                   age_high = max(age))

# Combine stats to table
stats_group$intervention = '-'
stats = data.table(rbind(stats_intervention, stats_group))
stats = stats[order(group, intervention)]

# Display descriptives
stats
```

## After exclusion {.tabset}

### Sample that completed the task

```{r}
# Get excludes based on function
excl_across = GetExcludes(modality = 'raw',
                          xval_split = 'fold',
                          buffering = TRUE,
                          reorganize = TRUE,
                          within_session = FALSE,
                          return_reasons = TRUE)
excl_across_reason = data.table(excl_across$reason)
excl_across = excl_across$excl
# Exclude CC group participants
excl_across_reason = excl_across_reason[id %in% data_demo$participant_id]
excl_across = excl_across[excl_across %in% data_demo$participant_id]

# Get excludes relating to task performance and scanner issues
basic = excl_across_reason[reason == 'incomplete_task']$id
perf = excl_across_reason[reason == 'task_performance']$id
scan = excl_across_reason[reason == 'pulse_fluctuations']$id

# Apply criteria
data_demo_excl = data_demo %>%
  filter(!participant_id %in% unique(basic))

stats_group_excl = data_demo_excl %>%
  group_by(group) %>%
  dplyr::summarise(n = length(age),
                   n_female = sum(female),
                   n_male = length(female) - sum(female),
                   perc_female = sum(female)/length(female),
                   age_mean = mean(age),
                   age_sd = sd(age),
                   age_low = min(age),
                   age_high = max(age))

stats_intervention_excl = data_demo_excl %>%
  group_by(group, intervention) %>%
  dplyr::summarise(n = length(age),
                   n_female = sum(female),
                   n_male = length(female) - sum(female),
                   perc_female = sum(female)/length(female),
                   age_mean = mean(age),
                   age_sd = sd(age),
                   age_low = min(age),
                   age_high = max(age))

# Combine stats to table
stats_group_excl$intervention = '-'
stats_excl = data.table(rbind(stats_intervention_excl, stats_group_excl))
stats_excl = stats_excl[order(group, intervention)]

# Display
stats_excl
```


### Excluding task performance/scanner issues

```{r}
# Apply criteria
data_demo_excl = data_demo %>%
  filter(!participant_id %in% unique(c(basic, perf, scan)))

stats_group_excl = data_demo_excl %>%
  group_by(group) %>%
  dplyr::summarise(n = length(age),
                   n_female = sum(female),
                   n_male = length(female) - sum(female),
                   perc_female = sum(female)/length(female),
                   age_mean = mean(age),
                   age_sd = sd(age),
                   age_low = min(age),
                   age_high = max(age))

stats_intervention_excl = data_demo_excl %>%
  group_by(group, intervention) %>%
  dplyr::summarise(n = length(age),
                   n_female = sum(female),
                   n_male = length(female) - sum(female),
                   perc_female = sum(female)/length(female),
                   age_mean = mean(age),
                   age_sd = sd(age),
                   age_low = min(age),
                   age_high = max(age))

# Combine stats to table
stats_group_excl$intervention = '-'
stats_excl = data.table(rbind(stats_intervention_excl, stats_group_excl))
stats_excl = stats_excl[order(group, intervention)]

# Display
stats_excl
```

### Across

```{r}
# Get excludes based on function
excl_across = GetExcludes(modality = 'raw',
                          xval_split = 'fold',
                          buffering = TRUE,
                          reorganize = TRUE,
                          within_session = FALSE,
                          return_reasons = TRUE)
excl_across_reason = data.table(excl_across$reason)
excl_across = excl_across$excl
# Exclude CC group participants
excl_across_reason = excl_across_reason[id %in% data_demo$participant_id]
excl_across = excl_across[excl_across %in% data_demo$participant_id]

# Apply criteria
data_demo_excl = data_demo %>%
  filter(!participant_id %in% excl_across)
```

```{r}
stats_group_excl = data_demo_excl %>%
  group_by(group) %>%
  dplyr::summarise(n = length(age),
                   n_female = sum(female),
                   n_male = length(female) - sum(female),
                   perc_female = sum(female)/length(female),
                   age_mean = mean(age),
                   age_sd = sd(age),
                   age_low = min(age),
                   age_high = max(age))

stats_intervention_excl = data_demo_excl %>%
  group_by(group, intervention) %>%
  dplyr::summarise(n = length(age),
                   n_female = sum(female),
                   n_male = length(female) - sum(female),
                   perc_female = sum(female)/length(female),
                   age_mean = mean(age),
                   age_sd = sd(age),
                   age_low = min(age),
                   age_high = max(age))

# Combine stats to table
stats_group_excl$intervention = '-'
stats_excl = data.table(rbind(stats_intervention_excl, stats_group_excl))
stats_excl = stats_excl[order(group, intervention)]

# Display
stats_excl
```

#### Exclusions and reasons {.tabset}

##### Task not completed

```{r}
excl_across_reason = data.table(excl_across_reason)
basic = excl_across_reason[reason == 'incomplete_task']$id
basic = unique(basic)
basic
```


##### Performance

```{r}
perf = excl_across_reason[reason == 'task_performance']$id
perf = unique(perf)
perf = perf[!perf %in% basic]
perf
```

##### Scanner issues

```{r}
scan = excl_across_reason[reason == 'pulse_fluctuations']$id
scan = unique(scan)
scan = scan[!scan %in% basic]
scan = scan[!scan %in% perf]
scan
```

##### Data issues

```{r}
data = excl_across_reason[reason %in% c('no_data', 'missing_buffer')]$id
data = unique(data)
data = data[!data %in% basic]
data = data[!data %in% perf]
data = data[!data %in% scan]
data
```

##### Overview

```{r}
final = data.frame('participant_id' = basic, 'reason' = 'incomplete_task')
final = rbind(final, data.frame('participant_id' = perf, 'reason' = 'task_performance'))
if(length(data) != 0){
  final = rbind(final, data.frame('participant_id' = scan, 'reason' = 'acquisition'))
}
if(length(data) != 0){
 final = rbind(final, data.frame('participant_id' = data, 'reason' = 'insufficient_data')) 
}
final %>%
  dplyr::group_by(reason) %>%
  dplyr::mutate(count = seq(length(reason)))
```


### Within

```{r}
# Get excludes based on function
excl_within = GetExcludes(modality = 'raw',
                          xval_split = 'sub_fold',
                          buffering = FALSE,
                          reorganize = TRUE,
                          within_session = TRUE,
                          return_reasons = TRUE)
excl_within_reason = data.table(excl_within$reason)
excl_within = excl_within$excl
# Exclude participants of CC group
excl_within_reason = excl_within_reason[id %in% data_demo$participant_id]
excl_within = excl_within[excl_within %in% data_demo$participant_id]

# Apply criteria
data_demo_excl = data_demo %>%
  filter(!participant_id %in% excl_within)
```

```{r}
stats_group_excl = data_demo_excl %>%
  group_by(group) %>%
  dplyr::summarise(n = length(age),
                   n_female = sum(female),
                   n_male = length(female) - sum(female),
                   perc_female = sum(female)/length(female),
                   age_mean = mean(age),
                   age_sd = sd(age),
                   age_low = min(age),
                   age_high = max(age))

stats_intervention_excl = data_demo_excl %>%
  group_by(group, intervention) %>%
  dplyr::summarise(n = length(age),
                   n_female = sum(female),
                   n_male = length(female) - sum(female),
                   perc_female = sum(female)/length(female),
                   age_mean = mean(age),
                   age_sd = sd(age),
                   age_low = min(age),
                   age_high = max(age))

# Combine stats to table
stats_group_excl$intervention = '-'
stats_excl = data.table(rbind(stats_intervention_excl, stats_group_excl))
stats_excl = stats_excl[order(group, intervention)]

# Display
stats_excl
```

#### Excludes and reason {.tabset}

##### Task not completed

```{r}
excl_within_reason = data.table(excl_within_reason)
basic = excl_within_reason[reason == 'incomplete_task']$id
basic = unique(basic)
basic
```


##### Performance

```{r}
perf = excl_within_reason[reason == 'task_performance']$id
perf = unique(perf)
perf = perf[!perf %in% basic]
perf
```

##### Scanner issues

```{r}
scan = excl_within_reason[reason == 'pulse_fluctuations']$id
scan = unique(scan)
scan = scan[!scan %in% basic]
scan = scan[!scan %in% perf]
scan
```

##### Data issues

```{r}
data = excl_within_reason[reason %in% c('no_data', 'missing_session')]$id
data = unique(data)
data = data[!data %in% basic]
data = data[!data %in% perf]
data = data[!data %in% scan]
data
```

##### Overview

```{r}
final = data.frame('participant_id' = basic, 'reason' = 'incomplete_task')
final = rbind(final, data.frame('participant_id' = perf, 'reason' = 'task_performance'))
if(length(scan) != 0){
  final = rbind(final, data.frame('participant_id' = scan, 'reason' = 'acquisition'))
}
final = rbind(final, data.frame('participant_id' = data, 'reason' = 'insufficient_data'))

final = setDT(final) %>%
  .[, count := seq(.N), by = reason]
final
```

